---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hsluv

<!-- badges: start -->
<!-- badges: end -->

The goal of hsluv is to provide a human-friendly alternative to HSL and HSV color spaces.

Human-friendly means that the same amount of numerical change in these spaces corresponds to about the same amount of visually perceived change.
This is not the case for HSL and HSV, which are based on RGB.


## Installation

You can install the development version of hsluv like so:

``` r
remotes::install_github("andrie/hsluv")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(hsluv)

# Convert hex to HSLuv
hex_to_hsluv("#ff0000")

# Convert HSLuv to hex
hsluv_to_hex(c(0, 100, 50))
```


## Credit

This project includes the [C implementation of HSluv](https://github.com/hsluv/hsluv-c), by Martin Mitáš, licensed under the MIT license:

Copyright © 2015 Alexei Boronine (original idea, JavaScript implementation)  
Copyright © 2015 Roger Tallada (Obj-C implementation)  
Copyright © 2017 Martin Mitáš (C implementation, based on Obj-C implementation)  

